Finding a closest point in a lattice of Voronoi's first kind

### 2014-01-08 paper.tex
minor
minor mods

It is necessary to introduce some notation.  For $S$ and subset of the indices $\{1,\dots,n+1\}$ let $I_S$ denote the column vector of length $n+1$ with $i$th element equal to one if $i \in S$ and $0$ otherwise.

@@

The paper describes an algorithm to compute a closest lattice point in a lattice of Voronoi's first kind when the obtuse superbasis is known~\cite{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases}.  The algorithm requires $O(n^4)$ operations where $n$ is the dimension of the lattice.  The algorithm iteratively computes a series of relevant vectors that converge to a closest lattice point after at most $n$ terms.   Each relevant vector in the series can be efficiently computed in $O(n^3)$ operations by computing a minimum cut in an undirected flow network.  The algorithm has potential application in communications engineering problems such as coding and quantisation.  An interesting problem for future research is to find lattices of Voronoi's first kind that produce good codes, good quantisers, or dense sphere packings~\cite{SPLAG,Conway1982VoronoiRegions}.

>>>>

It is necessary to introduce some notation.  For $S$ a subset of the indices $\{1,\dots,n+1\}$ let $I_S$ denote the column vector of length $n+1$ with $i$th element equal to one if $i \in S$ and $0$ otherwise. Thus, for example, $p+I_S$ denotes the vector $p$ with those elements having index from $S$ incremented by one.

@@

The paper describes an algorithm to compute a closest lattice point in a lattice of Voronoi's first kind when the obtuse superbasis is known~\cite{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases}.  The algorithm requires $O(n^4)$ operations where $n$ is the dimension of the lattice.  The algorithm iteratively computes a series of relevant vectors that converges to a closest lattice point after at most $n$ terms.   Each relevant vector in the series can be efficiently computed in $O(n^3)$ operations by computing a minimum cut in an undirected flow network.  The algorithm has potential application in communications engineering problems such as coding and quantisation.  An interesting problem for future research is to find lattices of Voronoi's first kind that produce good codes, good quantisers, or dense sphere packings~\cite{SPLAG,Conway1982VoronoiRegions}.
